\documentclass[10pt]{article}
\usepackage{hyperref}
\textheight=25.5cm
\textwidth=16.0cm
\oddsidemargin=-0.5cm
\topmargin=-2.0cm
\pagenumbering{arabic}
\bibliographystyle{unsrt}

\begin{document}

\noindent
\begin{center}
\emph{{\bf Curriculum Vitae}}\\
{{\Large\sc Jaime E. FORERO-ROMERO}}\\
\emph{Last updated on September 7, 2015}\\
\end{center}
\begin{minipage}{0.4\textwidth}
  \begin{flushleft}
    Calle 18A\# 1 - 10\\
    Bloque Ip, Of. 208\\
    Universidad de los Andes\\
    AA 4976, Bogot\'a, Colombia\\
  \end{flushleft}
\end{minipage}
\begin{minipage}{0.6\textwidth}
  \begin{flushright}
    {\it Nationality:} Colombian\\
    {\it Born:} October 14, 1981\\
    {\it telephone:} (+571) 3394949, Ext. 5183\\
    {\it email:} je.forero uniandes.edu.co\\    
    \url{http://wwwprof.uniandes.edu.co/~je.forero/}\\
    \url{http://github.com/forero}\\    
  \end{flushright}
\end{minipage}

\vspace{5mm}


\noindent{\Large\sc\bf Positions}\\
\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}%

\noindent $\bullet$ Associate Professor, Physics Department, \emph{Universidad de los Andes (Colombia)}, 8/2015-present\\

\noindent $\bullet$ Assistant Professor, Physics Department, \emph{Universidad de los Andes (Colombia)}, 8/2012-7/2015\\

\noindent $\bullet$ Gruber Fellow, Astronomy Department, \emph{University of California, Berkeley (USA)}, 10/2011-7/2012\\

\noindent $\bullet$  Postdoctoral Researcher, \emph{Leibniz Institute for
  Astrophysics-Potsdam (AIP) (Germany)}, 10/2007-9/2011  \\  



\noindent{\Large\sc\bf Education}\\
\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}%

\noindent$\bullet$\emph{\'Ecole Normale Sup\'erieure de Lyon (France)} (2005-2007)

PhD in Physics, December 2007\\

\noindent$\bullet$\emph{\'Ecole Normale Sup\'erieure (Ulm) (France)} (2003-2006)

  \'El\`eve S\'election Internationale

  M.Sc. in Physics (Magist\`ere Interuniversitaire), August 2005\\
  


\noindent$\bullet$\emph{Instituto Balseiro (Argentina)} (2001-2003)

  Undergraduate Physics studies (3$^{rd}$ and 4$^{th}$ years)\\

\noindent$\bullet$\emph{Universidad Nacional de Colombia} (1999-2001)

  Undergraduate Physics studies (1$^{st}$ and 2$^{nd}$ years)\\

\noindent{\Large\sc\bf Honors and Awards}\\
\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}%


\noindent$\bullet$ 2011. International Astronomical Union / Peter and Patricia Gruber Foundation Fellowship\\

\noindent$\bullet$ 2006-2007. Graduate Research Fellowship (Allocation Coupl\'ee) of the French Ministry for Research and Education.\\

\noindent$\bullet$ 2003-2006. Scholarship at the \'Ecole Normale Sup\'erieure (Paris), covers tuition fees plus room and board to pursue graduate studies and PhD research. \\

\noindent$\bullet$ 2001-2003. Undergraduate scholarship (covers tuition fees at the Instituto Balseiro plus room and board) from the Argentinian Atomic Energy
  Comission. \\

\noindent$\bullet$ 1999. Gold Medal in the National Chemistry Olympiad, Bogot\'a, Colombia (First Place, National Competition)\\


\noindent{\Large\sc\bf Research Interests}\\
\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}%

\noindent$\bullet$ Computational cosmology\\

\noindent$\bullet$ Large scale structure of the Universe\\

\noindent$\bullet$ Galaxy formation\\



\noindent{\Large\sc\bf Summary of Publication Record}\\
\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}%

\noindent$\bullet$ 24 Refereed journal articles in astrophysics since the first article in 2007.\\

\noindent$\bullet$ Total citations: 388. H-index: 10. (Source: Astrophysics Data System)\\

\noindent$\bullet$ Total citations: 409. H-index: 11. (Source: Google Scholar)\\


\noindent{\Large\sc\bf List of Significant Publications}\\
\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}%

\noindent$\bullet$ {\it A dynamical classification of the  cosmic web}.  {\bf Forero-Romero} J.E., Hoffman Y.,  Gottloeber S., Klypin A., Yepes G.,
MNRAS, 396, 1815-1824, 2009\\

\noindent$\bullet$ {\it A kinematic classification of the cosmic web},
  Y. Hoffman, O. Metuki , G. Yepes, S. Gottloeber, {\bf
    J. E. Forero-Romero}, N. I. Libeskind, A. Knebe, MNRAS, 425, 2049,
  2012 \\

\noindent$\bullet${\it The dark matter assembly of the Local Group in constrained cosmological   simulations of a $\Lambda$CDM universe} {\bf Forero-Romero} J.E.,  Hoffman Y., Yepes G., Gottl\"ober S., Piontek R., Klypin A., Steinmetz
M.,  MNRAS, 417, 1434, 2011 \\

\noindent$\bullet${\it {\tt CLARA}'s view on the escape fraction of Lyman-$\alpha$ photons in   high redshift galaxies} {\bf Forero-Romero} J.E., Yepes G., Gottl\"ober S., Knollmann S., Cuesta A., Prada F.,   MNRAS, 415, 3666, 2011\\

\noindent$\bullet${\it The MultiDark Database: Release of the Bolshoi and
  MultiDark Cosmological Simulations} , K. Riebe , A. M. Partl,
  H. Enke, {\bf J.E. Forero-Romero}, S. Gottloeber, A. Klypin,
  G. Lemson, F. Prada, J. R. Primack, M. Steinmetz, V. Turchaninov,
  Astronomische Nachrichten, 334, 691, 2013. \\




\end{document}

