\documentclass[9pt]{article}
\newcommand{\galics}{{\sc GalICS}}
\newcommand{\momaf}{{\sc MoMaF}}
\newcommand{\lemomaf}{{\sc LeMoMaF}}
%\textheight=25.5cm
%\textwidth=16.0cm
%\oddsidemargin=-0.5cm
%\topmargin=-2.0cm
\pagenumbering{arabic}
\bibliographystyle{unsrt}

\begin{document}

\noindent

%==================================WHOAMI===============================================
%\colorbox{gris-claro}{{\Large Jaime Ernesto FORERO ROMERO}}\\
\noindent
{{\Large Publication List - Jaime E. FORERO-ROMERO}}\\
%=================================NACIMIENTO============================================

\indent
Refereed Journal Articles
\begin{enumerate}
\item[] ADS statistics: 14 refereed articles since 2007. Total number of citations: 200. h-index: 9.
\item[14]{\it The MultiDark Database: Release of the Bolshoi and MultiDark Cosmological Simulations} , K. Riebe , A. M. Partl, H. Enke, {\bf J.E. Forero-Romero}, S. Gottloeber, A. Klypin, G. Lemson, F. Prada, J. R. Primack, M. Steinmetz, V. Turchaninov, Astronomische Nachrichten, 334, 691, 2013.

\item[13] {\it The kinematics of the Local Group in a cosmological context}, 
{\bf J.E. Forero-Romero}, Y. Hoffman, S. Bustamante, S. Gottloeber, G. Yepes, ApJ Letters, 767, 1, 2013

\item[12] {\it The velocity shear tensor: tracer of halo alignment}, Libeskind N., Hoffman Y., {\bf Forero-Romero} J.E., Gottloeber S., Knebe A., Steinmentz M., Klypin A., MNRAS 428, 2489, 2013

\item[11] {\it Effects of Star Formation Stochasticity on the Ly $alpha$ \& Lyman Continuum Emission from Dwarf Galaxies}, {\bf J. E. Forero-Romero} \& M. Dijkstra, MNRAS 428, 2163, 2013

\item[10] {\it A kinematic classification of the cosmic web}, Y. Hoffman, O. Metuki , G. Yepes, S. Gottloeber, {\bf J. E. Forero-Romero}, N. I. Libeskind, A. Knebe, MNRAS, 425, 2049, 2012

\item[9] {\it Modelling the fraction of Lyman Break Galaxies with strong Lyman-alpha emission at $5 < z < 7$} {\bf Forero-Romero J.E.}, Yepes G., Gottloeber S., Prada F., MNRAS, 419, 952, 2012

\item [8]
{\it The dark matter assembly of the Local Group in constrained cosmological
  simulations of a $\Lambda$CDM universe} {\bf Forero-Romero} J.E., Hoffman Y., Yepes G., Gottl\"ober S.,
  Piontek R., Klypin A., Steinmetz M., 
MNRAS, 417, 1434, 2011

\item[7] 
{\it Halo based reconstruction of the cosmic mass density field}
Mun\~oz-Cuartas J. C., M\"uller V, {\bf Forero-Romero} J. E.,
MNRAS, 417, 1303, 2011

\item [6]
{\it {\tt CLARA}'s view on the escape fraction of Lyman-$\alpha$ photons in
  high redshift galaxies}
{\bf Forero-Romero} J.E., Yepes G., Gottl\"ober S., Knollmann S., Cuesta A., Prada F.,  
MNRAS, 415, 3666, 2011

\item [5]
{\it Bullet Clusters in the MareNostrum Universe}. 
{\bf Forero-Romero} J.E., Yepes G., Gottl\"ober S., 
ApJ, 725, 1, 2010.

\item [4]
{\it Simulated vs. observed UV emission at high redshift: a hint for a clumpy
ISM? }. 
{\bf Forero-Romero} J.E., Yepes G., Gottl\"ober S., Knollmann S., Khalatyan A., Cuesta A., Prada F.,   MNRAS Letters, 403,  L31-L35, 2010

\item [3]
{\it The coarse geometry of merger trees in
  $\Lambda$CDM}.  {\bf Forero-Romero} J.E., 
MNRAS, 399, 762-768, 2009

\item [2]
{\it A Dynamical Classification of the  Cosmic Web}.  {\bf Forero-Romero} J.E., Hoffman Y.,  Gottloeber S., Klypin A., Yepes G.,
MNRAS, 396, 1815-1824, 2009

\item [1] 
{\it {\sc LeMoMaF}:  Lensed Mock Map Facility}. 
{\bf Forero-Romero} J.E., Blaizot J., Devriendt J., Van Waerbeke L., Guiderdoni B., 
MNRAS, 379. 1507-1518, 2007
\end{enumerate}




Non refereed 
\begin{enumerate}
\item[1] {\it Visualising Matter and Cosmologies: an Example Based on
  a Transhistorical Approach}, Lucia Ayala, Jaime E. Forero-Romero,
  Column 7, pp. 76-82 (2011) 
\end{enumerate}



\end{document}

